Binary companions of red giant stars in \apogee\ \DR

### 2018-02-26 paper/1-catalog/twoface-catalog.tex
MCMC section details

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to go process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
If just 1 posterior sample is returned after exhausting the full library of
prior samples, or if multiple (but fewer than \nposterior) are returned that all
lie within a single mode of the posterior pdf, the posterior pdf over orbital
parameters is treated as effectively unimodal: these stars are flagged ``needs
MCMC.''
If more than 1 posterior sample is returned after exhausting the full library of
prior samples, and the samples lie in multiple modes of the posterior pdf, the
only way to proceed is to generate more prior samples and continue running
\thejoker: these stars are flagged ``needs more prior samples.''

@@

In this case, we use the location of the returned sample, or a randomly chosen
sample from those returned to generate a small ball of initial conditions and
use standard MCMC to continue sampling until we obtain \nposterior\ samples.

We use an ensemble MCMC sampling algorithm (\citealt{Goodman:2010}) implemented
in \python\ (\citealt{Foreman-Mackey:2013}) for this step.
We run with 1024 walkers for 16384 steps, take the final walker positions, and
downsample until we have \nposterior\ samples.
\todo{We compute convergence statistics for each run and report whether the
chains appear converged or not.}

@@

We generate another equal-sized library of prior samples (a total of
$2\times\nprior$ samples) and continue sampling.
\todo{We note that because ... rejection sampling procedure, have to re-do
the rejection step after computing with full library of samples...}

>>>>

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to go process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
When this occurs, we continue sampling either using standard MCMC, or by
increasing the size of the prior cache and continuing rejection sampling with
\thejoker.

@@

If just one posterior sample is returned after exhausting the full library of
prior samples, or if multiple (but fewer than \nposterior) are returned that all
lie within a single mode of the posterior pdf, the posterior pdf over orbital
parameters is treated as effectively unimodal: these stars are flagged ``needs
MCMC.''
In this case, we use the location of the returned sample (if only one is
returned), or a randomly chosen sample from those returned (if multiple samples
are returned within one mode) to generate a small Gaussian ball of initial
conditions and use standard MCMC to continue sampling until we obtain
\nposterior\ samples.

We use an ensemble MCMC sampling algorithm (\citealt{Goodman:2010}) implemented
in \python\ (\package{emcee}; \citealt{Foreman-Mackey:2013}) to perform the
samplings.
We transform the standard Keplerian orbital parameters to a safer
parametrization, $(\ln P, \sqrt{K}\,\cos M_0, \sqrt{K}\,\sin M_0, \sqrt{e}\,\cos
\omega, \sqrt{e}\,\cos \omega, \ln s^2, v_0)$, to sample in.
This reparametrization is safer and more efficient for sampling with
\package{emcee}, which expects parameters to be components of a vector so that
linear operations can be applied (see, e.g., \citealt{Hogg:2017}); the angle
variables $(\omega, M_0)$ don't meet this requirement in the standard
parametrization.
We use the same prior pdfs as in \thejoker\ when running MCMC (see
\tablename~\ref{tbl:params}).

For each star that is flagged ``needs MCMC,'' we run \package{emcee} with 1024
walkers for 16384 steps, take the final walker positions, and downsample at
random until we have \nposterior\ samples.
We compute the Gelman--Rubin convergence statistic, $\hat{R}_j$,
(\citealt{Gelman:1992}) for each parameter $j$ and include these values in the
catalogs below when standard MCMC is run.
We also provide a binary flag, ``converged,'' for each sampling continued with
MCMC that is set to true if:
\begin{equation}
\underset{j}{\textrm{mean}}\left(\hat{R}_j\right) < 1.1 \quad .
\end{equation}

@@

If more than one posterior sample is returned after exhausting the full library
of prior samples, and the samples lie in multiple modes of the posterior pdf,
the only way to proceed is to generate more prior samples and continue running
\thejoker: these stars are flagged ``needs more prior samples.''
In this case, we generate another equal-sized library of prior samples (a total
of $2\times\nprior$ samples) and continue rejection sampling.
\todo{We note that because ... rejection sampling procedure, have to re-do
the rejection step after computing with full library of samples...}
